\section*{Optimization Problem — Button Press Counters}

\subsection*{Problem Description}
We are given a finite set of buttons. Pressing a button increments a fixed subset of counters by one.
Each button may be pressed any non-negative integer number of times.
Given a target vector specifying the desired final value of each counter, the objective is to reach the target using the minimum total number of button presses.

\subsection*{Variables}
Let $x\in\mathbb{Z}_{\geq0}$ denote the number of times button $j$ is pressed.

\subsection*{Data}
Let $A_{k,j}\in\{0,1\}$ be the incidence matrix, where
\begin{equation}
    A_{k,j} = 
    \begin{cases}
    1 
    0  
    \end{cases}
\end{equation}

Let $t_k\in\mathbb{Z}_{\geq0}$ denote the target value of counter $k$.

\subsection*{Constraints}
For each counter $k$, the total number of increments must equal the target
\begin{equation}
    \sum_j A_{k,j}x_j = t_k
\end{equation}
 
\subsection*{Objective}
Minimize the total number of button presses:
\begin{equation}
    \min \sum_j x_j    
\end{equation}

\subsection*{Optimization Type}
This problem is an \emph{Integer Linear Program (ILP)} with:
\begin{itemize}
\item Linear objective
\item Linear equality constraints
\item Non-negative integer decision variables
\end{itemize}

\subsection*{Solution Approach Using GLPK}
The problem can be solved using the GNU Linear Programming Kit (GLPK) as a mixed-integer program.
\begin{enumerate}
\item Introduce one integer variable $x_j$ per button.
\item Add one equality constraint per counter.
\item Set the objective to minimize $\sum_j x_j$.
\item Solve the resulting MIP using GLPK's integer optimizer.
\end{enumerate}

\subsection*{Remarks}
\begin{itemize}
\item The formulation is efficient due to the small number of buttons and moderate target values.
\item The constraint matrix is sparse and binary.
\item This approach applies to the counting version of the problem.
\item The on/off (parity) version of the problem belongs to linear algebra over $\mathbb{F}_2$and is better solved using bitwise methods rather than ILP.
\end{itemize}